%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Christian Juresh} \\ \vspace{4pt}
    \small 07977 977 877 $|$ \href{mailto:christianjuresh@gmail.com}{\underline{christianjuresh@gmail.com}} $|$ 
    \href{https://linkedin.com/in/chrisJuresh}{\underline{linkedin.com/in/chrisJuresh}} $|$
    \href{https://github.com/chrisJuresh}{\underline{github.com/chrisJuresh}} \\ \vspace{4pt}
    \href{https://instagram.com/christian.juresh}{\underline{instagram.com/christian.juresh}} $|$
    \small \textbf{Fluent in:} English, Russian, Ukrainian $|$
    \small London, UK
\end{center}

\vspace{-18pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Queen Mary University of London}{Sep. 2021 -- May 2024}
      {{\normalfont BSc Hons in Computer Science, 1st (82.4\%) }}{}
      \resumeItem{EECS Final Year Project Prize for Outstanding Achievement (92.7\%)}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart


    \resumeSubheading
      {Third Bridge Group Limited}{Sep. 2024 -- Present}
      {Integration Engineer}{London, UK}
      \resumeItemListStart
\resumeItem{Developed BigQuery Python scripts for Marshall Wace and D.E. Shaw to process client data.}
\resumeItem{Introduced Black, isort and pre-commits, ensuring compatibility with existing flake8 and CI/CD configuration.}
\resumeItem{Refactored and redeployed cronjobs and services to a new Google Cloud cluster, projected to save £500 a month}
\resumeItem{Responsible for engineering business workflows, integrating internal and third-party systems, and supplying critical data to internal business intelligence platforms, dashboards and slack alerts.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Royal College of Radiologists}{Aug. 2022 -- Sep. 2024}
      %{Lead Professional Services Administrator}{London, UK}
      {Professional Services Administrator}{London, UK}
      \resumeItemListStart
      
\resumeItem{Independently managed and completed the job plan evaluation process for consultant radiologist and oncologist vacancies across 104+ NHS Trusts, coordinating with HR personnel and Regional Specialty Advisors.}
\resumeItem{Collaborated with NHS services to assign the most suitable RCR representatives for consultant appointment panels from a database of over 360 doctors, automating the majority of the process using Python’s Flask framework.}
\resumeItem{Developed Excel spreadsheets with intelligent algorithms to enhance data organisation, processing, and analysis - reducing the time required for a full-time position by 60\% and assisting various colleagues.}
\resumeItem{Introduced VBA, Power Query, PivotTables, and Python’s pandas and Matplotlib for data analysis and reporting.}
\resumeItem{Formulated and documented system requirements for a CRM built on Dynamics365 and SharePoint.}
\resumeItem{Consulted the software and database design for a medical AI tools registry.}
      \resumeItemListEnd
      

    \resumeSubheading
      {Royal College of Obstetricians and Gynaecologists}{Jul. 2024 -- Sep. 2024}
      {Workforce and Professionalism Assistant}{London, UK}
      \resumeItemListStart
\resumeItem{Consulted on and took part in the job plan review and Advisory Appointment Committee service.}
\resumeItem{Collated and presented figures to a panel of Doctors to support the bestowal of awards and up to £18,900 in prizes using abstract management software and data analysis, tracking insights for 387 submissions.}
\resumeItem{Automated and optimised various administrative processes using PivotTables and complex Excel formulas}
  \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Queen Mary University of London}{Sep. 2022 -- Apr. 2024}
      {Computer Science Demonstrator}{London, UK}
      \resumeItemListStart
\resumeItem{Provided support to first- and second-year university students, and graded coursework for modules including: \\ Professional and Research Practice, Procedural Programming (Java), and Graphical User Interfaces (React.js).}
    \resumeItemListEnd

%     \resumeSubheading
%       {Office Angels}{Jun. 2022 -- Nov. 2022}
%       {Front Desk Reception / Finance Administrator}{London, UK}
%       \resumeItemListStart
% \resumeItem{Supported employees at Office Concierge (White Collar Factory), Quarto Publishing, and Four Marketing.}
% \resumeItem{Cleared a 2-year backlog of 135 invoices at Speakers Corner by applying effective database principles in Excel.}
%       \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      
    
      \resumeProjectHeading
          {\textbf{Royal College NHS Jobs Audit Automation} $|$ \emph{Python, BeautifulSoup, numpy, pandas, tkinter, sklearn.}}{}
          \resumeItemListStart
          
\resumeItem{Designed a program to automate job plan audits for Royal Colleges, allowing a bi-monthly weeklong process at the RCOG to be completed monthly automatically, and providing the RCR with long-needed but previously unobtainable insights.}
\resumeItem{Built a BS4 web scraper to extract valuable data from hundreds of jobs, including the job description documents.}
\resumeItem{Implemented a fuzzy matching algorithm to match the job descriptions to an internal archive of thousands of documents, utilising multithreading due to the high volume of data, and supporting a variety of file formats.}
\resumeItem{Utilised Python to transform and visualise data for reporting.}

            \resumeItemListEnd

            \resumeProjectHeading
      {\textbf{RCR JD \& AAC Prototype Site} $|$ \emph{Python, django-ninja, JavaScript/TypeScript, SvelteKit, Linux, Nginx, SQL, Certbot, Zod}}{}
      \resumeItemListStart
        \resumeItem{Developed a fully functional prototype website to automate job description reviews and advisory appointment committee panels for the Royal College of Radiologists. Achieved 92.7\% for the dissertation and source code.}
        \resumeItem{Created a full-stack web application with django-ninja serving a REST API and SvelteKit as the frontend. Implemented robust security measures with SSL, and JWT authentication with email verification through PostMark.}
        \resumeItem{Designed a highly relational database schema, using Pydantic for API data validation, and OpenAPI-Typescript to transfer type checking alongside data from backend to frontend with a custom API consumption library.}
        \resumeItem{Used PyTransitions to create object-oriented finite state machines to enforce strict workflows, and pioneered fully dynamic grid forms in Superforms, with custom validation settings per cell defined in an admin panel in accordance to WCAG 2.2.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
    %-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: 
     Python, 
     JavaScript/TypeScript, 
     SQL, 
     R,  
     Bash, 
     Java, 
     VBA, 
     XQuery, 
     HTML, 
     CSS, 
     PHP, 
     XML.
     } \\
     \textbf{Frameworks}{: 
     Django (DRF \& ninja), 
     SvelteKit, 
     BigQuery,
     PyTorch, 
     scikit-learn, 
     TailwindCSS, 
     Spark, 
     Vue3, 
     React, 
     Flask.
     } \\
     \textbf{Tools}{: 
     Linux, 
     Git, 
     CI/CD,
     Docker,
     Kubernetes,
     GCP,
     Nginx, 
     UML, 
     Excel, 
     Power Query, 
     GnuPG, 
     Teams, 
     Photoshop, 
     Lightroom. 
     } \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}